Windowed least-squares model reduction for dynamical systems

### 2019-10-18 section4/spatial_numerical.tex
up

\subsection{\spatialAcronym\ trial subspaces: indirect solution approach}\label{sec:indirect}
\KTC{This is a fantastic insight and a really great contribution!}
In contrast to the direct approach,
indirect methods ``indirectly" solve the minimization
problem~\eqref{eq:tclsrm} by solving the Euler--Lagrange
equations~\eqref{eq:lspg_continuous}--\eqref{eq:lspg_adjoint} associated with
stationarity. The
system associated with the Euler--Lagrange equations comprises a coupled two-point boundary value
problem. Several techniques have
been devised to solve such problems, 
including shooting methods, multiple shooting
methods~\cite{multiple_shooting}, and the forward--backward sweep
method~\cite{fbs} (FBSM).  This work explores using the FBSM.

@@

The FBSM is an iterative approach that can be used to
solve the two-point boundary value problem. The general process of the FBSM is
as follows: First, the system~\eqref{eq:lspg_continuous} is (numerically) solved forward in
time using an initial guess to the costate to obtain an initial guess to
the generalized coordinates. Next, the adjoint equation~\eqref{eq:lspg_adjoint} is solved \textit{backwards} in time given the
approximation to the generalized coordinates. This gives a new estimate to the
costate, which is then used to again solve the forward problem to obtain
a new estimate of the generalized coordinates. This process is continued until
convergence. Algorithm~\ref{alg:st_iter} outlines the method. The algorithm
contains three parameters: the relaxation factor $\rho \le 1$, the growth factor
$\fbsmGrowth \ge 1$, and the decay factor $\fbsmDecay \ge 1$. The relaxation factor controls the rate at which the costate seen by~\eqref{eq:lspg_continuous} is updated. The
closer $\rho$ is to unity, the faster the algorithm will converge.
For large window sizes, however, too high a value of $\rho$ can lead to an unstable iterative process. 
A proper value of $\rho$ can be
obtained with a line search. The line search presented in Algorithm~\ref{alg:st_iter} adapts the relaxation factor
according to the objective. Convergence properties of the FBSM method are
presented in Ref.~\cite{McAsey2012ConvergenceOT}. It is shown that, for a small 
enough value of $\rho$, the algorithm will converge.

>>>>

\subsection{\spatialAcronym\ trial subspaces: indirect solution approach}\label{sec:indirect}
In contrast to the direct approach,
indirect methods ``indirectly" solve the minimization
problem~\eqref{eq:tclsrm} by solving the Euler--Lagrange
equations~\eqref{eq:lspg_continuous}--\eqref{eq:lspg_adjoint} associated with
stationarity. This
system comprises a coupled two-point boundary value
problem. Several techniques have
been devised to solve such problems, 
including shooting methods, multiple shooting
methods~\cite{multiple_shooting}, and the forward--backward sweep
method~\cite{fbs} (FBSM).  This work explores using the FBSM.

@@

Until convergence, the FBSM alternates between solving the
system~\eqref{eq:lspg_continuous} \textit{forward} in time given a fixed value
of the costate, and solving the adjoint equation~\eqref{eq:lspg_adjoint}
\textit{backward} in time given a fixed value for the generalized coordinates.
Typically, the system~\eqref{eq:lspg_continuous} is solved first given an
initial guess for the costate.
%
%consists of the following steps. First, the
%system~\eqref{eq:lspg_continuous} is (numerically) solved \textit{forward} in
%time using an initial guess of the costate to obtain an initial solution for
%the generalized coordinates. Next, given this initial solution for the
%generalized coordinates, the adjoint equation~\eqref{eq:lspg_adjoint} is
%solved \textit{backward} in time for an updated costate solution.
%approximation to the generalized coordinates. This gives a new estimate to the
%costate, which is then used to again solve the forward problem to obtain
%a new estimate of the generalized coordinates. This process is continued until
%convergence. 
Algorithm~\ref{alg:st_iter} outlines the algorithm, which 
contains three parameters: the relaxation factor $\rho \le 1$, the growth factor
$\fbsmGrowth \ge 1$, and the decay factor $\fbsmDecay \ge 1$. The relaxation factor controls the rate at which the costate seen by~\eqref{eq:lspg_continuous} is updated. The
closer $\rho$ is to unity, the faster the algorithm will converge.
For large window sizes, however, a large a value of $\rho$ can lead to an unstable iterative process. 
In practice, a line search is used to compute an acceptable value for the
relaxation factor $\rho$. The line search presented in Algorithm~\ref{alg:st_iter} adapts the relaxation factor
according to the objective. Convergence properties of the FBSM method are
presented in Ref.~\cite{McAsey2012ConvergenceOT}, which shows that the
algorithm will converge for a sufficiently small 
value of $\rho$.
